Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-19 manuscript/manuscript.tex
Small edits.

\subsection*{Results On Real Metagenomic Datasets}
We evaluated the performance of approximate betweenness centrality algorithms on metagenomic stool sample.
We compared the performance of these algorithms with Bambus2's repeat detection module.
Bambus2's repeat detection module took over 50 hours to find repeats in the assembly graph.
The algorithm based on sampling shortest paths took 312.69 seconds for $\epsilon = 0.1$.
The algorithm based on sampling nodes took 469 seconds for the sample of 1,000 nodes and approximately 1.3 hours for the 10,000 node sample. Therefore, we can conclude that the approximation algorithms offers significant speedup for repeat finding.

>>>>

\subsection*{Results On Real Metagenomic Datasets}
We evaluated the performance of approximate betweenness centrality algorithms on metagenomic stool sample.
We compared the performance of these algorithms with Bambus2's repeat detection module.
Bambus2's repeat detection module took over 50 hours to find repeats in the assembly graph.
The algorithm based on sampling shortest paths took 313 seconds for $\epsilon = 0.1$.
The algorithm based on sampling nodes took 469 seconds for the sample of 1,000 nodes and approximately 1.3 hours for the 10,000 node sample. Thus, the approximation algorithms offer significant speedups for repeat finding.
